I express my deepest gratitude to all those who have contributed to the completion of this dissertation, as their support and encouragement have been invaluable throughout this academic journey.
First and foremost, I extend my sincere appreciation to my advisor, Professor Toshiyuki Amagasa, for his unwavering guidance, patience, and expertise. Their insightful feedback and constructive criticism have played a pivotal role in shaping the content and direction of this research.
I am grateful to the members of my dissertation committee for their time, expertise and valuable insights. Their diverse perspectives enriched the quality of this work and provided me with a broader understanding of the subject matter.

I would like to express my heartfelt gratitude to Dr. Masashi Ishii for his invaluable support and guidance during my time at NIMS (National Institute for Materials Science).
This research has greatly benefited from fruitful discussions and collaboration with Sae Dieb and Guillaume Lambard. 
I owe my ability to steer my career towards academic research in computer science and machine learning to the invaluable guidance, assistance, and support of Dr. Patrice Lopez. Over the course of more than a decade, Dr. Lopez has been a constant source of inspiration, providing me with the necessary tools and motivation to pursue my academic endeavours.
I express my gratitude to Dr. Laurent Romary for his assistance during my time at the National Institute for Research in Digital Science and Technology (INRIA) in Paris. Additionally, I am thankful to Dr. Mikiko Tanifuji for her support during my remarkable journey to Japan. 

I have been fortunate to have many individuals who have had a positive impact on my career, life, and accomplishments. Unfortunately, I am unable to mention each of them individually due to space constraints.